First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-01-20 eg6-letters/DVCS-coh-He4/dvcs_he4_prl.tex
update the experimental setup part in the coherent prl paper

\begin{figure}[tb]
\includegraphics[width=6.5cm,angle=-90]{figs/RTPC.pdf}
\vspace{-0.9cm}
\caption{Left: A picture of the CLAS-EG6 RTPC before insertion into the 
   solenoid.  Right: A cross section of the CLAS-EG6 RTPC perpendicular to the 
beam direction. An illustration of a $^4$He track originating from the 
pressurized straw target is shown along with the electrons produced in the 
drift region.}
\label{fig:RTPC}
\end{figure}

@@

>>>>

The experiment, CLAS-EG6, took place in the experimental Hall-B of Jefferson 
labortory (JLab) in 2009. JLab delivers, simultaneously, a nearly 100\% duty 
factor polarized electrons into three experimental Halls (A, B, C). The data 
were collected over three months via projecting a 6.064 GeV longitudinally 
ploarized beam, (83$\%$ polarization), on a 6 atm gasous $^4$He target.  The 
Hall-B Large Acceptance Spectrometer (CLAS) basic desing \cite{CLAS_ref} was 
upgraded, during the CLAS-E1DVCS1 experimental run \cite{Girod:2007aa} in 2005, 
with a specially designed electromagnetic calorimeneter, Inner calorimeter 
(IC). The IC has extended the photon detection acceptance of CLAS, which is 
origionally from 15$^{\circ}$ to 45$^{\circ}$, to polar angle reach as minimum 
as 4$^{\circ}$. During the same experiment, a 5 Tesla solenoid was added around 
the target to shield the inner detectors from the low-energy M\o ller 
electrons.

At 6 GeV incident electron beam energy, the recoil $^4$He nuclei, from the 
coherent DVCS channel, have an average momentum (per charge) around 125 MeV/c, 
while the CLAS spectrometer detects charged particles with a threshold of 250 
MeV/c. In order to ensure the exculsitivy of the our coherent DVCS channel, we 
built a small and light radial time projection chamber (RTPC) to detect 
recoiling nuclei down to energies of few MeVs. Figure~\ref{fig:RTPC} presents 
our cylinderical RTPC, which is 20 cm long and 15 cm diameter, surrounding the 
$^4$He gaseous target, with a 3 cm radial drift length. The detector was 
specifically calibrated for $^4$He nuclei using elastic scattering produced 
with a 1.2~GeV electron beam.

\begin{figure}[tb]
\includegraphics[width=7.0cm,angle=-90]{figs/RTPC.pdf}
\vspace{-0.9cm}
\caption{Left: A picture of the CLAS-EG6 RTPC before insertion into the 
   solenoid.  Right: A cross section of the CLAS-EG6 RTPC perpendicular to the 
beam direction. An illustration of a $^4$He track originating from the 
pressurized straw target is shown along with the electrons produced in the 
drift region.}
\label{fig:RTPC}
\end{figure}

To ensure that the process is exclusive, we apply cuts on several kinematic 
variables (figure~\ref{fig:kin-cuts}) such as missing energy,
mass and momentum. The cuts are chosen to represent consistently 3 half width 
at half maximum in order to avoid any bias in the selection.

@@

\bibitem{CLAS_ref}
   B.A. Mecking {\it et al.}, Nucl.\ Inst.\ and Meth.\ A 503, 513 (2003).
